Cryptanalysis of SBC based post-quantum signature scheme

### 2025-06-20 rapport.tex
manque expand et punctured keys
minor changes

	To lighten the notation, we will not write the index of the round, but all the sharing elements are per round $e \in [1, \tau]$.

@@

				\item Compute $X_1, X_2, Y_1, Y_2$ \\
				\quad $X_1 \leftarrow \sum_{i=1}^{N} X_1^{\lir}$. \\
				\quad $X_2 \leftarrow \sum_{i=1}^{N} X_2^{\lir}$. \\
				\quad $Y_1 \leftarrow \sum_{i=1}^{N} Y_1^{\lir}$. \\
				\quad $Y_2 \leftarrow \sum_{i=1}^{N} Y_2^{\lir}$.
			\end{enumerate}

@@

			\vspace{0.5em}
			\textbf{Phase 3: Simulation of the MPC protocol.} For each $e \in [1:\tau]$:
			\begin{enumerate}[label=\arabic*.]
				\item Compute $A$ and $B$ and share them: \\
				\quad $A \leftarrow X_1Y_1 - X_2Y_2$. \\
				\quad $B \leftarrow X_1(\vec{v} \cdot \vec{y}) + Y_1(\vec{u} \cdot \vec{x}) - X_2(\vec{u} \cdot \vec{y}) - Y_2(\vec{v} \cdot \vec{x})$. \\
				\quad $\delta_A \leftarrow A - \sum_{i=1}^{N} R_A^{\lir}$. \\
				\quad $\delta_B \leftarrow B - \sum_{i=1}^{N} R_B^{\lir}$. \\

				\item Compute the commitments \\
				\quad $View_i \leftarrow (
				t_0^{\lir},
				(X_1 + t_0(\vec{u} \cdot \vec{x}))^{\lir},
				(X_2 + t_0(\vec{v} \cdot \vec{x}))^{\lir},
				(Y_1 + t_0(\vec{v} \cdot \vec{y}))^{\lir},
				(Y_2 + t_0(\vec{u} \cdot \vec{y}))^{\lir},
				(A + t_0 B)^{\lir}
				)$. \\
				\quad $\texttt{com}^{[e]} := \text{Hash}_0(e, View_1, \dots, View_N, \vec{\delta}_x, \vec{\delta}_y, \delta_A, \delta_B)$
			\end{enumerate}

>>>>

	To simplify the notation, we omit the round index when it is clear from context. Unless stated otherwise, all sharing-related elements are defined per round $e \in [1, \tau]$.

	We denote by $\mathcal{K}^e$ the punctured key corresponding to round $e$. This punctured key represents the co-path in the GGM tree used to derive the associated random values.

	The function Expand is a generic function, that expands the hash to extract different psuedo-random values from it.

@@

				\item Compute $X_1, X_2, Y_1, Y_2$ \\
				\quad $X_1 \leftarrow \sum_{i=1}^{N} X_1^{\lir}$. \\
				\quad $X_2 \leftarrow \sum_{i=1}^{N} X_2^{\lir}$. \\
				\quad $Y_1 \leftarrow \sum_{i=1}^{N} Y_1^{\lir}$. \\
				\quad $Y_2 \leftarrow \sum_{i=1}^{N} Y_2^{\lir}$.

				\item Compute $A$ and $B$ and share them: \\
				\quad $A \leftarrow X_1Y_1 - X_2Y_2$. \\
				\quad $B \leftarrow X_1(\vec{v} \cdot \vec{y}) + Y_1(\vec{u} \cdot \vec{x}) - X_2(\vec{u} \cdot \vec{y}) - Y_2(\vec{v} \cdot \vec{x})$. \\
				\quad $\delta_A \leftarrow A - \sum_{i=1}^{N} R_A^{\lir}$. \\
				\quad $\delta_B \leftarrow B - \sum_{i=1}^{N} R_B^{\lir}$.
			\end{enumerate}

@@

			\vspace{0.5em}
			\textbf{Phase 3: Simulation of the MPC protocol.} For each $e \in [1:\tau]$:
			\begin{enumerate}[label=\arabic*.]
				\item Compute the commitments \\
				\quad $View_i \leftarrow (
				t_0^{\lir},
				(X_1 + t_0(\vec{u} \cdot \vec{x}))^{\lir},
				(X_2 + t_0(\vec{v} \cdot \vec{x}))^{\lir},
				(Y_1 + t_0(\vec{v} \cdot \vec{y}))^{\lir},
				(Y_2 + t_0(\vec{u} \cdot \vec{y}))^{\lir},
				(A + t_0 B)^{\lir}
				)$. \\
				\quad $\texttt{com}^{[e]} := \text{Hash}_0(e, View_1, \dots, View_N, \vec{\delta}_x, \vec{\delta}_y, \delta_A, \delta_B)$
			\end{enumerate}
